The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
fix refs fst par intro

## Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1993;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009; @Mayor_2007; @Sugihara_1989], habitat selection, and food webs.
Meanwhile, in the context of animal behaviour, certain behaviours are scale
dependent, for example, acoustic communication in birds occurs over variable
spatial scales [@Luther_2009]. We posit that animal behaviour and, more
specifically, the social environment that animals experience must also be
scale-dependent.

>>>>

## Introduction
Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
Meanwhile, in the context of animal behaviour, certain behaviours are scale
dependent, for example, acoustic communication in birds occurs over variable
spatial scales [@Luther_2009]. We posit that animal behaviour and, more
specifically, the social environment that animals experience must also be
scale-dependent.
